\section{Definition of Python}

Python is a high-level, interpreted programming language that is widely used for
general-purpose programming. It emphasizes code readability and allows programmers
to write clear and logical programs using a simple and structured syntax.

\subsection{Features of Python}

\begin{itemize}
  \item \textbf{Simple and Readable Syntax}  
        Python uses an English-like syntax, which makes programs easy to read and write.

  \item \textbf{High-Level Language}  
        Python hides complex details of the system, allowing programmers to focus on problem solving.

  \item \textbf{Interpreted Language}  
        Python programs are executed line by line, which makes debugging easier.

  \item \textbf{Object-Oriented}  
        Python supports object-oriented concepts such as classes and objects.

  \item \textbf{Portable (Platform Independent)}  
        Python programs can run on different operating systems without any modification.

  \item \textbf{Extensive Library Support}  
        Python provides a large standard library that supports various programming tasks.

  \item \textbf{Open Source}  
        Python is free to use and distribute.
\end{itemize}


\subsection{Compiler}

A compiler is a program that translates the entire source code written in a
high-level programming language into machine code at once. The generated machine
code is saved as an executable file, which can be run later.

\textbf{Examples:} C, C++

\begin{itemize}
  \item Translates the whole program at one time
  \item Produces an executable file
  \item Errors are reported after compilation
\end{itemize}


\subsection{Interpreter}

An interpreter is a program that translates and executes source code line by line.
It does not create a separate executable file. Each line is analyzed and executed
immediately.

\textbf{Examples:} Python, JavaScript
\begin{itemize}
  \item Translates and executes code line by line
  \item No separate executable file is generated
  \item Easier to debug compared to compiled languages
\end{itemize}

