\chapter{IDLE in Python}
\section{IDLE in Python}

\textbf{IDLE} stands for \textbf{Integrated Development and Learning Environment}.

IDLE is the \textbf{default tool} that comes with Python.
It is mainly used by beginners to write and run Python programs.

\begin{itemize}
  \item It comes free with Python installation.
  \item It has a Python shell to run code line by line.
  \item It has a simple editor to write Python files.
  \item It shows errors clearly.
\end{itemize}

\textbf{Note:}  
IDLE is good for learning Python, not for big projects.

\section{IDE (Integrated Development Environment)}

An \textbf{IDE} is a complete software used for coding, testing, and debugging.

\begin{itemize}
  \item It supports many programming languages.
  \item It has code editor, debugger, terminal, and tools.
  \item It is used for professional and large projects.
\end{itemize}

\textbf{Examples:}
\begin{itemize}
  \item PyCharm
  \item VS Code
  \item Eclipse
\end{itemize}

\section{Text Editor}

A \textbf{Text Editor} is a simple tool to write plain text or code.

\begin{itemize}
  \item It cannot run programs by itself.
  \item It does not show detailed errors.
  \item It is very lightweight.
\end{itemize}

\textbf{Examples:}
\begin{itemize}
  \item Notepad
  \item Notepad++
  \item Sublime Text
\end{itemize}

\section{Difference Between IDE, IDLE, and Text Editor}

\begin{tabular}{|l|l|l|l|}
\hline
\textbf{Feature} & \textbf{IDE} & \textbf{IDLE} & \textbf{Text Editor} \\
\hline
Purpose & Full development & Learning Python & Writing text/code \\
\hline
Run Code & Yes & Yes & No \\
\hline
Debugger & Yes & Basic & No \\
\hline
Complex Projects & Yes & No & No \\
\hline
Ease of Use & Medium & Very Easy & Very Easy \\
\hline
\end{tabular}

\section*{Summary}

\begin{itemize}
  \item \textbf{IDE} = Professional tool for big projects.
  \item \textbf{IDLE} = Simple Python tool for learning.
  \item \textbf{Text Editor} = Only for writing text.
\end{itemize}